---
title: "p8105_hw7_cgd2137"
author: "Carolina Downie"
date: "11/18/2017"
output: html_document
---

##Problem 1


```{r loading iris dataset}
library(ggplot2)
library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

Showing work for creation of function for replacing missing data in iris dataset (if necessary)
```{r build-up to function}
#If I was dealing with an individual vector
mean_Sepal.Length<-iris_with_missing$Sepal.Length %>% mean(na.rm = TRUE) %>% round(., 1)

virginica<-c("virginica")

#This takes an individual vector and returns an individual vector
iris_with_missing$Sepal.Length %>% replace(., is.na(iris_with_missing$Sepal.Length), mean_Sepal.Length)

iris_with_missing$Species %>% replace(., is.na(iris_with_missing$Species), virginica)


```

Now what we want to do to this is generalize it so that it can be appplied across all the columns using the map function. 
The inputs that are required:

* dataframe

* replacement value (changes depending on numeric or character), but this is created within function

* column name (changes)

```{r Problem 1 function}

replace_missing<- function(df) {
  mean_value <- df %>% mean(na.rm = TRUE) %>% round(., 1)
  virginica<-c("virginica")
  
  if (is.character(df)) {
    df %>% replace(., is.na(df), virginica)
  } else if (is.numeric(df)) {
    df %>% replace(., is.na(df), mean_value)
  }
}

replace_missing(iris_with_missing)

```

Applying replace_missing function to iris_with_missing_dataset
```{r replacing missing in iris_with_missing dataset}

iris_replace_missing <- map(iris_with_missing, replace_missing) %>% data.frame()
```


```{r function with different summary statements}

replace_missing_update<- function(df, summary_stat) {
  
  summary_value <- df %>% summary_stat(., na.rm = TRUE) %>% round(., 1)
  virginica<-c("virginica")
  
  if (is.character(df)) {
    df %>% replace(., is.na(df), virginica)
  } else if (is.numeric(df)) {
    df %>% replace(., is.na(df), summary_value)
  }
}

```


```{r replace missing with mean} 

iris_replace_missing_mean <- map(iris_with_missing, replace_missing_update, mean) %>% data.frame()

iris_replace_missing_median <- map(iris_with_missing, replace_missing_update, median) %>% data.frame()

```


##Problem 2

This problem uses the Airbnb data.

Load and tidy the data as needed for analysis. Nest columns within boro and describe the resulting data frame.

Using mutate + map (and other functions as necessary), fit models for rental price as an outcome using rating and room type as predictors. Extract the results of your modeling and unnest the result. Present the results of your analysis, using text, tables, and figures as appropriate.

```{r loading and tidying airbnb data}
library(janitor)
airbnb_data <- read_csv("../data/nyc_airbnb.csv") %>%
  clean_names() %>%
  mutate(rating = review_scores_location / 2) %>%
  select(boro = neighbourhood_group, neighbourhood, rating, price, room_type,
         latitude, longitude)
```


```{r nesting data frame in boro}
airbnb_data_nest<-nest(airbnb_data, neighbourhood:longitude)


```

Nesting the airbnb_data dataset within boro results in a new dataset with 5 observations and 2 variables: borough name (boro), and the corresponding list columns (data) that contain all the information about neighborhoods, rating, price, room_type, latitude, and longitude for each borough. 


*Rental Price by Rating*

This is a continuous predictor variable 
```{r fitting model for rental price by rating}
#Rating

   airbnb_data_nest %>%
  mutate(model = map(data, ~lm(price ~ rating, data = .x)), 
         results = map(model, broom::tidy)) %>%
  select(-data, -model) %>%
  unnest() %>% knitr::kable()
  


airbnb_data %>%
  ggplot(aes(x = rating, y = price, group = boro, color = boro)) + 
    geom_point() + 
    geom_smooth(method = "lm", formula = y ~ x) +
  facet_grid(. ~boro) + 
  labs(
    title = "Plot of rental price by rating") +
   theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
The table of slope and intercept values, and the plots show that for all boroughs except Staten Island, there is a positive relationship between rating and price. 

*Rental Price by Room Type*

This is a categorical variable with three possible options: entire home/apt, private room, or shared room, therefore we need 2 dummy variables (k-1). When we run the linear model, "Entire home/apt" is set as the reference variable. 
```{r fitting model for rental prices}
#Room Type
  airbnb_data_nest %>%
  mutate(model = map(data, ~lm(price ~ room_type, data = .x)), 
         results = map(model, broom::tidy)) %>%
  select(-data, -model) %>%
  unnest() %>% knitr::kable()
  

airbnb_data %>%
  ggplot(aes(x = room_type, y = price, group = boro, color = boro)) + 
    geom_point() + 
    geom_smooth(method = "lm", formula = y ~ x) +
  facet_grid(. ~boro) + labs(
    title = "Plot of rental price by room_type") +
   theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

The table of slope and intercept values and the plots show that for all 5 boroughs, there is a negative relationship between price and room type when room_type "Entire house/apartment" is the reference value. 


##Problem 3
When designing an experiment or analysis, a common question is whether it is likely that a true effect will be detected – put differently, whether a false null hypothesis will be rejected. The probability that a false null hypothesis is rejected is referred to as power, and it depends on several factors, including: the sample size; the effect size; and the error variance. In this problem, you will conduct a simulation to explore power in a multiple linear regression.

First set the following design elements:

Fix n=30
Fix xi1
 and xi2
 as draws from independent standard normal distributions
 
 Fix β0=1
 and β1=1
.
Fix σ2=50
Next, set β2=0
. Generate 10000 datasets from the model
```{r creating function to simulate regression model}
sim_regression <- function(n, beta0, beta1, beta2, var) {
  sim_data <- tibble(
    xi1 = rnorm(n, 0, 1),
    xi2 = rnorm(n, 0,1),
    y= beta0 +beta1*xi1 + beta2*xi2 + rnorm(n, 0, var)
  )
  ls_fit = lm(y ~ xi1 + xi2, data = sim_data)

  tibble(
  beta2_real = beta2,
  beta2_hat=summary(ls_fit)$coefficients[3,1], 
  pvalue = summary(ls_fit)$coefficients[3,4]
  
  )  
}

beta2_0<-rerun(5,sim_regression(n=30, beta0=1, beta1=1, beta2 = 0, var = 50)) %>% bind_rows()

```

Repeat the above for β2={1,2,3,4,5,6}--since we're going to be repeating this multiple times, we should make a function and use a map function to apply it across multiple options for beta2

```{r creating function for running regression model, applying it across different beta2 using map function}

simulate_beta2<- function(n_rep, beta2) {
  rerun(n_rep, sim_regression(n=30, beta0=1, beta1=1, beta2, var = 50)) %>% bind_rows()
}

beta2_options<-c(0:6)
beta2_estimates<-map_df(beta2_options, simulate_beta2, n_rep = 1000)

```

***Note: I used 1000 here instead of 10000 because when I tried 10000 it took over 15 minutes and still didn't load, so I stopped trying. 

Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of β2
 on the x axis. Describe the association between effect size and power.
 
```{r}

beta2_estimates %>% group_by(beta2_real) %>%
  mutate(n_tests = n()) %>%
 filter(pvalue < 0.05) %>%
  group_by(beta2_real) %>%
  mutate(reject = n(), power = reject/n_tests) %>% 
  select(beta2_real, power) %>% 
  unique() %>%
  ggplot(aes(x = beta2_real, y = power)) + 
  geom_bar(stat = "identity") + labs(
    title = "Plot of the power of the test versus the true beta2 value"
  )


```


This plot shows that in general, as effect size increases, the power increases. 



 
Make a plot showing the average estimate of β̂2
 on the y axis and the true value of β2
 on the x axis. 
```{r}
 
beta2_hat<-beta2_estimates %>% group_by(beta2_real) %>%
  mutate(mean_beta2 = mean(beta2_hat), variable = "mean_beta2_hat") %>%
  select(beta2_real, mean_beta2, variable) %>%
  unique() 
  
beta2_reject<-beta2_estimates %>% filter(pvalue < 0.05) %>% 
  group_by(beta2_real) %>%
  mutate(mean_beta2 = mean(beta2_hat), variable = "mean_beta2_reject") %>%
  select(beta2_real, mean_beta2, variable) %>%
  unique() 
 
beta2_summary<-rbind(beta2_hat, beta2_reject) 

beta2_summary %>% 
  ggplot(aes(x = beta2_real, y = mean_beta2, col = variable)) + 
  geom_point() + labs(
    title = "Plot of the true value of beta2 versus the mean estimated beta2 value"
  )
```



As this plot shows, the sample averages of beta2_hat across tests for which the null is rejected are not approximately equal to the true value of β2. This makes sense--in order for the null hypothesis that β2=0 to be rejected, we would expect that the estimated β2 is far from zero. 



##Problem 4

```{r Problem 4 function}

library(modelr)

sim_df_const_function <- function(n_samp){
  set.seed(1)
  tibble(
  x = rnorm(n_samp, 1, 1),
  error = rnorm(n_samp, 0, 1),
  y = 2 + 3 * x + error
)
}

sim_df_const_function(25) %>%
  bootstrap(n = 5000) %>% 
  mutate(models = map(strap, ~lm(y ~ x, data = .x)), 
         results = map(models, broom::tidy)) %>%
  select(results) %>% 
  unnest() %>%
  select(term, estimate) %>%
  group_by(term) %>%
  mutate(test_id = c(1:n())) %>%
  spread(term, estimate) %>%
  rename(beta0_hat = '(Intercept)', beta1_hat = 'x') %>%
  mutate(theta_hat = log(beta0_hat/beta1_hat)) %>%
  ggplot(aes(x = theta_hat)) +
  geom_histogram() + labs(
    title = "Distribution of theta_hat when n_sample = 25, bootstrap 5000 times"
  )


```

```{r making this into a function}
#Since we're repeating this process more than 3 times, we need to write another function:

sim_df <- function(n_samp, n) {
  
  sim_df_const_function(n_samp) %>%
  bootstrap(n) %>% 
  mutate(models = map(strap, ~lm(y ~ x, data = .x)), 
         results = map(models, broom::tidy)) %>%
  select(results) %>% 
  unnest() %>%
  select(term, estimate) %>%
  group_by(term) %>%
  mutate(test_id = c(1:n())) %>%
  spread(term, estimate) %>%
  rename(beta0_hat = '(Intercept)', beta1_hat = 'x') %>%
  mutate(theta_hat = log(beta0_hat/beta1_hat)) %>%
  ggplot(aes(x = theta_hat)) +
  geom_histogram() 
}

```




```{r Problem 4 n_sample is 50 }

sim_df(n_samp=50, n=5000) + labs(title = "Distribution of theta_hat when n_samp = 50 and n=5000")

```

```{r Problem 4 n_sample is 250}

sim_df(n_samp=250, n=5000) + labs(title = "Distribution of theta_hat when n_samp = 250 and n=5000")


```



As we can see from these plots, as n_sample, sample size of the simulated dataset increases, the distributions of theta_hat become less skewed (the tails on both sides are more even), and the distributions shift to the left (more negative), which means that beta0_hats are smaller than beta1_hats, since it is on the log scale. 

**Question: is is appropriate that the bootstrap number is 1000? Should it be changed? 
Changing 1000 to 5000 produces tighter plots. 